Concurrent Programming with Harmony

### 2020-08-12 book/paper.tex
Updated alloc module

The \texttt{alloc} module
\index{alloc module}%
support thread-safe (but not interrupt-safe) dynamic allocation of
dictionaries.  There are just two methods:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{malloc()} & allocate a dictionary \\
\hline
\texttt{free($r$)} & free an allocated dictionary $r$ \\
\hline
\end{tabular}
\vspace{1em}

>>>>

The \texttt{alloc} module
\index{alloc module}%
maintains a pool of ``memory locations'' and
supports thread-safe (but not interrupt-safe) dynamic allocation of
memory locations.  There are just two methods:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{malloc()} & allocate and return a pointer to a memory location \\
\hline
\texttt{free($p$)} & free an allocated memory location $p$ \\
\hline
\end{tabular}
\vspace{1em}
